---
title: "Statistical Inference Course Project"
author: "KKher"
date: "7/18/2020"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Overview

In this project you will investigate the exponential distribution in R and compare it with the Central Limit Theorem. The second portion of the project, we're going to analyze the ToothGrowth data in the R datasets package.

```{r cars}
library(ggplot2)
library(dplyr)
```

## Part 1: Simulation Exercise Instructions

The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. 
- Has mean = 1/lambda & standard deviation = 1/lambda. 
- Set lambda = 0.2 
- Investigate the distribution of averages of 40 exponentials. 
- Note that you will need to do a 1000 simulations.

```{r Exponential Simulation}
lambda = 0.2

# theoretical Mean & standard deviation
actual_mean = 1/0.2
actual_sd = 1/0.2

# simulate 1000 
sample_means = NULL
for (i in 1 : 1000) sample_means = c(sample_means, mean(rexp(40, lambda)))
ggplot() +
  aes(sample_means) +
  geom_histogram(fill="#69b3a2", color="#e9ecef", alpha=0.9) + 
  ggtitle("Distribution of 1000 simulations of averages of 40 exponentials") +
  geom_vline(xintercept = mean(sample_means), color="blue")
```

Actual Mean = ```r actual_mean``` and the simulated mean = ```r mean(sample_means)```

Actual sd = ```r actual_sd``` and the simulated mean = ```r sd(sample_means)```


## Part 2: Basic Inferential Data Analysis Instructions
### Load the ToothGrowth data and perform some basic exploratory data analyses

``` {r toothGrowth_Data}
data(ToothGrowth)
```

### Provide a basic summary of the data.

``` {r toothGrowth_EDA}
head(ToothGrowth)
summary(ToothGrowth)
str(ToothGrowth)

# plot len & supp
ggplot(data=ToothGrowth) + 
  aes(x=supp, y=len)+
  geom_boxplot(aes(fill=supp)) +
  facet_grid(cols = vars(dose)) +
  ggtitle("Length-Supplement Relation split by dose")

```

> From Figure above, mean seems to be equal for both supp only for dose=2.

### Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)

``` {r toothGrowth_CI}
# create t test

# perform t test between supp types where dose = 2
t.test(ToothGrowth$len[ToothGrowth$supp=="OJ" & ToothGrowth$dose==2], ToothGrowth$len[ToothGrowth$supp=="VC" & ToothGrowth$dose==2], paired = TRUE)

# perform t test between supp types where dose != 2
t.test(ToothGrowth$len[ToothGrowth$supp=="OJ" & ToothGrowth$dose!=2], ToothGrowth$len[ToothGrowth$supp=="VC" & ToothGrowth$dose!=2], paired = TRUE)

```

### State your conclusions and the assumptions needed for your conclusions.

If we consider Null Hypothesis (H0) to be; mean is almost equal per supp per dose

1- We Fail to reject H0 where dose = 2, as t-value is very small and is equal to ```r t.test(ToothGrowth$len[ToothGrowth$supp=="OJ" & ToothGrowth$dose==2], ToothGrowth$len[ToothGrowth$supp=="VC" & ToothGrowth$dose==2], paired = TRUE)$statistic ```

2- We reject H0 where dose does not equal to 2, as t-value is large enough and is equal to ```r t.test(ToothGrowth$len[ToothGrowth$supp=="OJ" & ToothGrowth$dose!=2], ToothGrowth$len[ToothGrowth$supp=="VC" & ToothGrowth$dose!=2], paired = TRUE)$statistic ```