---
title: "Statistical Inference Course Project - Part1"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Overview

In this project you will investigate the exponential distribution in R and compare it with the Central Limit Theorem. 

```{r cars}
library(ggplot2)
library(dplyr)
```

## Part 1: Simulation Exercise Instructions

The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. 
- Has mean = 1/lambda & standard deviation = 1/lambda. 
- Set lambda = 0.2 
- Investigate the distribution of averages of 40 exponentials. 
- Note that you will need to do a 1000 simulations.

```{r Exponential Simulation}
lambda = 0.2

# theoretical Mean & standard deviation
actual_mean = 1/0.2
actual_sd = 1/0.2

# simulate 1000 
sample_means = NULL
for (i in 1 : 1000) sample_means = c(sample_means, mean(rexp(40, lambda)))
ggplot() +
  aes(sample_means) +
  geom_histogram(fill="#69b3a2", color="#e9ecef", alpha=0.9) + 
  ggtitle("Distribution of 1000 simulations of averages of 40 exponentials") +
  geom_vline(xintercept = mean(sample_means), color="blue")
```

Actual Mean = ```r actual_mean``` and the simulated mean = ```r mean(sample_means)```

Actual sd = ```r actual_sd``` and the simulated mean = ```r sd(sample_means)```
