---
title: "Statistical Inference Course Project - Part2"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Overview

The second portion of the project, we're going to analyze the ToothGrowth data in the R datasets package.

```{r cars}
library(ggplot2)
library(dplyr)
```
## Part 2: Basic Inferential Data Analysis Instructions
### Load the ToothGrowth data and perform some basic exploratory data analyses

``` {r toothGrowth_Data}
data(ToothGrowth)
```

### Provide a basic summary of the data.

``` {r toothGrowth_EDA}
head(ToothGrowth)
summary(ToothGrowth)
str(ToothGrowth)

# plot len & supp
ggplot(data=ToothGrowth) + 
  aes(x=supp, y=len)+
  geom_boxplot(aes(fill=supp)) +
  facet_grid(cols = vars(dose)) +
  ggtitle("Length-Supplement Relation split by dose")

```

> From Figure above, mean seems to be equal for both supp only for dose=2.

### Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)

``` {r toothGrowth_CI}
# create t test

# perform t test between supp types where dose = 2
t.test(ToothGrowth$len[ToothGrowth$supp=="OJ" & ToothGrowth$dose==2], ToothGrowth$len[ToothGrowth$supp=="VC" & ToothGrowth$dose==2], paired = TRUE)

# perform t test between supp types where dose != 2
t.test(ToothGrowth$len[ToothGrowth$supp=="OJ" & ToothGrowth$dose!=2], ToothGrowth$len[ToothGrowth$supp=="VC" & ToothGrowth$dose!=2], paired = TRUE)

```

### State your conclusions and the assumptions needed for your conclusions.

If we consider Null Hypothesis (H0) to be; mean is almost equal per supp per dose

1- We Fail to reject H0 where dose = 2, as t-value is very small and is equal to ```r t.test(ToothGrowth$len[ToothGrowth$supp=="OJ" & ToothGrowth$dose==2], ToothGrowth$len[ToothGrowth$supp=="VC" & ToothGrowth$dose==2], paired = TRUE)$statistic ```

2- We reject H0 where dose does not equal to 2, as t-value is large enough and is equal to ```r t.test(ToothGrowth$len[ToothGrowth$supp=="OJ" & ToothGrowth$dose!=2], ToothGrowth$len[ToothGrowth$supp=="VC" & ToothGrowth$dose!=2], paired = TRUE)$statistic ```